### 2018-07-13 FrascatiPlot/Paper/NucleiB2.tex
Correcting typos spotted by Andreas

\section{Introduction} 
The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions. In addition, these studies might shed light on the internal structure of the formed objects themselves. 
In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e. the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.  
The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei. This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm \cite{Nemura:1999qp}. Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.

@@

To this purpose, we compare to models the existing data from the LHC. For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size. 
In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities. The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}. In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach. 
The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios. As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments. 
In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

@@

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

@@

This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations. The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e. the centrality dependence) and that of the (hyper-)nucleus. In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.

>>>>

\section{Introduction} 
The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions. In addition, these studies might shed light on the internal structure of the formed objects themselves. 
In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e. the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.  
The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei. This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}. Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.

@@

To this purpose, we compare to models the existing data from the LHC. For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size. 
In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities. The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}. In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach. 
The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios. As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments. 
In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

@@

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

@@

This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations. The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e. the centrality dependence) and that of the (hyper-)nucleus. In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.
